Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-15 latex/main.tex
Updates from Overleaf
Fix fig reference

\begin{figure}
\centering
\includegraphics[width=\linewidth]{robust_vs_artificial_classification}
\caption{
Classification of ``robust'' and artifactual recombination events.
Scatterplot of recombination events by the net number of supporting loci
for the left parent (x-axis) and for the right parent (y-axis). The shaded
regions highlight artifactual recombination events, which have fewer than four
net supporting loci on one side or both sides of the suggested breakpoint.
Colors indicate the primer scheme used for sequencing. The pie charts show
breakdowns of the recombination events by primer scheme per quadrant.
Recombination events associated with the origins of Pango Xs are labeled.
}
\label{fig:recombinant_qc}
\end{figure}

@@

\begin{figure}
\centering
% NOTE the size of the second "m" column doesn't matter, but we have to fix the
% size in order for vertical centering to work :sigh:
% The layout here isn't ideal, but it's incredibly fiddly to get center
% alignment veritically with cells to work, so this is good enough.
\begin{tabularx}{0.85\textwidth}{>{\centering\arraybackslash}m{1cm}>{\arraybackslash}m{1cm}}
% FIXME: these samples are chosen randomly and so almost certainly do not
% belong to the correct quadrants.
Q1 & \includegraphics[height=\cprheight]{static/causedby-ERR10306608.png}\\
Q2 & \includegraphics[height=\cprheight]{static/causedby-SRR15864165.png}\\
Q3 & \includegraphics[height=\cprheight]{static/causedby-ERR6760245.png}\\
Q4 & \includegraphics[height=\cprheight]{static/causedby-SRR21087725.png}\\
\end{tabularx}
\caption{Examples of problematic copying patterns. A-D are examples drawn from
the labeled quadrants in Figure~\ref{fig:recombinant_qc}.}
\label{fig:copying_pattern_examples}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/recombinant_qc}
\caption{
Classification of ``robust'' and artifactual recombination events.
Scatterplot of recombination events by the net number of supporting loci
for the left parent (x-axis) and for the right parent (y-axis). The shaded
regions highlight artifactual recombination events, which have fewer than four
net supporting loci on one side or both sides of the suggested breakpoint.
Colors indicate the primer scheme used for sequencing. The pie charts show
breakdowns of the recombination events by primer scheme per quadrant.
Recombination events associated with the origins of Pango Xs are labeled.
}
\label{fig:recombinant_qc}
\end{figure}

@@

\begin{figure}
\centering
% NOTE the size of the second "m" column doesn't matter, but we have to fix the
% size in order for vertical centering to work :sigh:
% The layout here isn't ideal, but it's incredibly fiddly to get center
% alignment veritically with cells to work, so this is good enough.
\begin{tabularx}{0.85\textwidth}{>{\centering\arraybackslash}m{1cm}>{\arraybackslash}m{1cm}}
Q1 & \includegraphics[height=\cprheight]{static/causedby-ERR10306608.png}\\
Q2 & \includegraphics[height=\cprheight]{static/causedby-SRR15864165.png}\\
Q3 & \includegraphics[height=\cprheight]{static/causedby-ERR6760245.png}\\
Q4 & \includegraphics[height=\cprheight]{static/causedby-SRR21087725.png}\\
\end{tabularx}
\caption{
Examples of copying patterns.
Q1 to Q4 are examples drawn from
the labeled quadrants in Figure~\ref{fig:recombinant_qc}.
Q2 illustrates a marginally good copying pattern.
Q1, Q3, and Q4 illustrate copying patterns that fail the QC thresholds.
}
\label{fig:copying_pattern_examples}
\end{figure}
